---
title: "Week4"
author: "Chirag Vithalani"
date: "November 22, 2015"
output: html_document
---
Problem :
Exploratory Data Analysis in R. Choose an interesting dataset and use R graphics to describe the data. You may
use base R graphics, or a graphics package of your choice. You should include at least one example of each of the
following:
1. histogram
2. boxplot
3. scatterplot

Solution :

Install required packages first

```{r}
install.packages("devtools", dependencies = TRUE, repos = "http://lib.stat.cmu.edu/R/CRAN/")
library(RCurl)
```
I found "The California Test Score Data Set" intresting, so using that data and printing head
```{r}
california_school_CSV <- getURL("https://raw.githubusercontent.com/vincentarelbundock/Rdatasets/master/csv/Ecdat/Caschool.csv")
california_school_data <- read.csv(text = california_school_CSV, header = TRUE, stringsAsFactors = FALSE)
head(california_school_data)
```

Print graphics

```{r}
hist(california_school_data$teachers, col = "lightblue", breaks = 100, main = "Number of Teachers in California Schools")
four_counties_of_california_school <- california_school_data [which(california_school_data$county == "Kings" |california_school_data$county == "Los Angeles" |california_school_data$county == "Kern" |california_school_data$county == "San Diego" ),]
boxplot(enrltot~county, data = four_counties_of_california_school, main = "Total Enrollments in Four California Counties")

plot(california_school_data$enrltot, california_school_data$teachers, main = "Total Enrollment vs. Number of Teachers")
```

Summary :

Number of schools have smaller numbers of teachers


