---
title: "Week4"
author: "Chirag Vithalani"
date: "November 22, 2015"
output: html_document
---
Problem :
Exploratory Data Analysis in R. Choose an interesting dataset and use R graphics to describe the data. You may
use base R graphics, or a graphics package of your choice. You should include at least one example of each of the
following:
1. histogram
2. boxplot
3. scatterplot

Solution :

Install required packages first

```{r}
install.packages("devtools", dependencies = TRUE, repos = "http://lib.stat.cmu.edu/R/CRAN/")
library(RCurl)
```
I found "The California Test Score Data Set" intresting, so using that data and printing head
```{r}
caschooldata <- getURL("https://raw.githubusercontent.com/karenweigandt/cuny-summer-bridge/master/Caschoolincolumns.csv")
ca_school_data_csv <- read.csv(text = caschooldata, header = TRUE, stringsAsFactors = FALSE)
head(ca_school_data_csv)
```

Print graphics

```{r}
hist(ca_school_data_csv$teachers, col = "lightblue", breaks = 100, main = "Number of Teachers in California Schools")
four_counties_of_ca_school <- ca_school_data_csv [which(ca_school_data_csv$county == "Kings" |ca_school_data_csv$county == "Orange" |ca_school_data_csv$county == "Fresno" |ca_school_data_csv$county == "Yuba" ),]
boxplot(enrltot~county, data = four_counties_of_ca_school, main = "Enrollment Totals in Four California Counties")

plot(ca_school_data_csv$enrltot, ca_school_data_csv$teachers, main = "Enrollment Total vs. Number of Teachers")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
